GRASS: Distinguishing Planet-induced Doppler Signatures from Granulation with a Synthetic Spectra Generator

### 2022-09-06 src/tex/ms.tex
[showyourwork] overleaf sync

% Main body with filler text
%% === introduction === 
\section{Introduction} \label{intro}
Since the detection of the first exoplanet orbiting a main sequence star \citep{Mayor1995}, the radial velocity (RV) method has enabled the discovery of several hundred planets to date \citep[see the NASA Exoplanet Archive;][]{Akeson2017}. Despite these successes, the RV method will \revise{need additional development to address stellar variability} and characterize Earth-analog planets around solar-type stars. In principle, the RV method uses the planet-induced Doppler reflex motion of host stars to infer the existence of planetary companions. In practice, the host stars exhibit intrinsic astrophysical variability that complicate or preclude the measurement of minute reflex velocities due to smaller, Earth-mass planets. Although advances in instrumentation have dramatically improved spectrograph stability and spectral sensitivity, the challenges posed by intrinsic stellar variability remain a significant barrier to the discovery of lower-mass, rocky planets \revise{in or near the habitable zone of other stellar systems.} \par

@@

%input{captions/fig4.tex}
\revise{To create synthetic spectra, \grass\ creates disk-resolved line profiles on a uniform spatial grid (as described in \S\ref{sec:resolved_disk}).} The \revise{ideal resolution of this spatial grid over the stellar surface would match that of the input observations. However, because the spatial resolution of the input observations was designed to approximate the typical angular area of supergranules and consequently varies with position on the disk (as described in \S\ref{subsec:input_data}), simulating an ideal grid is impractical.} Therefore, we choose \revise{a rectangular grid and set} $N$ \revise{(the number of grid cells along each Cartesian $xy$ direction in the sky plane) such that the area of the spatial grid cell matches the weighted-average area of the input data observations. Given the sizes of the elliptical oscillations described in \S\ref{subsec:input_data} and \citetalias{Lohner-Bottcher2018}, we compute $N^2\sim132^2$ as our optimized number of grid cells.} \par

@@

\subsection{Synthetic Line Depth and RV Variability} \label{sec:depth_var}
%input{captions/fig5.tex}

@@

%input{captions/fig6.tex}

@@

%input{captions/fig7.tex}

>>>>

%% === introduction === 
\section{Introduction} \label{intro}
Since the detection of the first exoplanet orbiting a main sequence star \citep{Mayor1995}, the radial velocity (RV) method has enabled the discovery of several hundred planets to date \citep[see the NASA Exoplanet Archive;][]{Akeson2017}. Despite these successes, the RV method will \revise{need additional development to address stellar variability} and characterize Earth-analog planets around solar-type stars. In principle, the RV method uses the planet-induced Doppler reflex motion of host stars to infer the existence of planetary companions. In practice, the host stars exhibit intrinsic astrophysical variability that complicate or preclude the measurement of minute reflex velocities due to smaller, Earth-mass planets. Although advances in instrumentation have dramatically improved spectrograph stability and spectral sensitivity, the challenges posed by intrinsic stellar variability remain a significant barrier to the discovery of lower-mass, rocky planets \revise{in or near the habitable zone of other stellar systems.} \par

@@

%input{captions/fig4.tex}
\begin{figure}
    \epsscale{1.2}
    \plotone{figures/fig4.pdf}
    \caption{Effect of simulation spatial grid size on the generated synthetic spectra. Points indicate the mean RMS calculated from many RV time series, and error bars \revise{the standard error of the mean}. \revise{Two measurements of the RV variability from solar granulation are shown as the orange forward-hatched \citep{Elsworth1994} and green back-hatched \citep{Palle1999} regions. We find that our ideal grid size of $N^2 = 132^2$ (vertical dashed line), chosen to produce grid cells with angular area matching the weighted-average spatial resolution of the input observations, intersects the power law relation within the  \citet{Palle1999} region.} \revise{At spatial resolutions greater than $N\sim~400$, the angular size of the grid cells becomes much smaller than that of the smallest-footprint input observations and consequently loses physical validity.}}
    \label{fig:res}
    \script{fig4_plot.jl}
\end{figure}{}

\revise{To create synthetic spectra, \grass\ creates disk-resolved line profiles on a uniform spatial grid (as described in \S\ref{sec:resolved_disk}).} The \revise{ideal resolution of this spatial grid over the stellar surface would match that of the input observations. However, because the spatial resolution of the input observations was designed to approximate the typical angular area of supergranules and consequently varies with position on the disk (as described in \S\ref{subsec:input_data}), simulating an ideal grid is impractical.} Therefore, we choose \revise{a rectangular grid and set} $N$ \revise{(the number of grid cells along each Cartesian $xy$ direction in the sky plane) such that the area of the spatial grid cell matches the weighted-average area of the input data observations. Given the sizes of the elliptical oscillations described in \S\ref{subsec:input_data} and \citetalias{Lohner-Bottcher2018}, we compute $N^2\sim132^2$ as our optimized number of grid cells.} \par

@@

\subsection{Synthetic Line Depth and RV Variability} \label{sec:depth_var}
%input{captions/fig5.tex}
\begin{figure}
    \epsscale{1.2}
    \plotone{figures/fig5.pdf}
    \caption{Doppler velocity variability weakly scales with synthetic line depth \revise{for lines deeper than 20\% of continuum level.} As in Figure \ref{fig:res}, points indicate the mean RMS calculated from many RV time series, and error bars the \revise{standard error of the mean}. \revise{The shaded blue region encloses 68\% of all RMS values across all runs.} From line depths of 0.5\% to 20\%, the RMS of an RV time series obtained from \grass\ output spectra appears to decrease. From 20\% to 95\% depth, the RMS then appears to steadily increase. However, the shallowest lines (gray \revise{hatched} region) are synthesized exclusively from extrapolated input data \revise{(see Figure \ref{fig:two} and associated text)}. The trend in this region may therefore be unreliable.} 
    \label{fig:rms_vs_depth}
    \script{fig5_plot.jl}
\end{figure}

@@

%input{captions/fig6.tex}
\begin{figure}
    \epsscale{1.2}
    \plotone{figures/fig6.pdf}
    \caption{RV time-series variability and stellar inclination. As in Figure \ref{fig:res}, points indicate the mean RMS calculated from many RV time series, and error bars the standard \revise{error of the mean}. \revise{As in Figure \ref{fig:rms_vs_depth}, the shaded blue region encloses 68\% of all RMS values across all runs.} Equator-on stars do not appear to show any significant difference in \revise{granulation-driven} RV variability compared to pole-on stars. Additionally, \revise{neither the width} of the RV RMS \revise{distributions (blue shaded region)} \revise{nor the error on the mean (error bars)} appear to scale with inclination, suggesting that the impact of additional uncertainty introduced by a broader CCF profile for the Sun when viewed equator-on is \revise{small in comparison to the variability introduced by granulation signals.}}
    \label{fig:inclination}
    \script{fig6_plot.jl}
\end{figure}{}

@@

%input{captions/fig7.tex}
\begin{figure*}
    \epsscale{1}
    \plotone{figures/fig7.pdf}
    \caption{Distributions of \revise{mean} velocities measured from many realizations of synthetic observing programs. The number of exposures, each lasting \revisetwo{300} seconds, is varied between panels, as annotated in the upper right of each panel. \revise{For each given realization of a synthetic observation program, the velocities measured within the same night are averaged. Each distribution is built up from these averaged velocity measurements.} The black histograms correspond to simulated observing plans with short, 30-second lags between simulated exposures. The blue histograms correspond to long, \revise{60}-minute lags between simulated exposures. The \revise{relative} values of \revise{the} measured \revise{velocities} are themselves arbitrary, and correspond to the difference in rest-frame and CCF-template wavelengths. As expected, the distributions visibly narrow as the number of exposures is increased. \revisetwo{However, there is no significant difference in the width of the short-wait and long-wait distributions in all panels (see Table \ref{tab:obs}),} \revise{in apparent disagreement with past studies which have shown that long waits between observations produced lower scatter in measured RVs \citep[e.g.,][]{Dumusque2011, Meunier2015, CollierCameron2019}.} In the future, input data spanning longer than 20 minutes would allow a more robust comparison of observing strategies\revise{, since our short baseline input data do not preserve longer timescale variability (e.g., as in supergranulation)}.}
    \label{fig:obs}
    \script{fig7_plot.jl}
\end{figure*}
